---
title: "Regression and Statistical Inference"
author: "Shashidhar Cheeti"
---

# Assignmnet

```{r}
# Load the Library
library(tidyverse)
```

```{r}
# Load the file
car_prices <- readRDS("Causal_Data_Science_Data/car_prices.rds")
# Create a Data Frame
df=data.frame(car_prices)
```

1. Check the dimensions
```{r}
dim(df)
```
There are 181 rows and 22 columns in the data file.

2. Using appropriate commands to get a more detailed look at the data.
```{r}
head(df)
```

```{r}
glimpse(df)
```

```{r}
summary(df)
```
The data types present are character and numeric data type. The numbers differ from string regarding the type of information represented. Numeric data is used for quantitative measurements, while character data is used for textual information.


3. Linear regression
```{r}
lm_all <- lm(price ~ ., data = df)
summary(lm_all)
```
As from the summary of linear regression, All factors estimate with a p-value less than 0.05(arbitrary significance level-alpha) are relevant for the pricing of a car like carbodyhatchback, carbodywagon, enginelocationrear, carwidth, enginetypeohc, enginetypeohcv, cylindernumberfive, cylindernumberfour, cylindernumbersix, cylindernumbertwelve, enginesize, stroke and peakrpm.

4. Choosing one regressor
```{r}
lm_imp <- lm(price ~ carwidth, data = df)
summary(lm_imp)
```

```{r}
# 1. Data type and what value it can take on
str(car_prices$carwidth)
# 2. Effect it has on the price and what changing the value would have as a result
summary(lm_all)$coefficients['carwidth',]
# 3. Whether its effect is statistically significant
summary(lm_all)$coefficients['carwidth','Pr(>|t|)']
```

4.1 The regressor used was car width and it belongs to the numeric variables (discrete/continuous). It can take numeric values.

4.2 As our estimate is positive (2859.5), we have a positive effect. As a result increasing the car width would increase the price of the car.

4.3 Yes, it is statistically significant as the p value is lower than our significance level (0.05)

5. Add a variable seat_heating to the data
```{r}
df_new <- df %>% mutate(seatheating = TRUE)
df_new
```

```{r}
# New regression
lm_new <- lm(price ~ seatheating , data = df_new)
summary(lm_new)
```
There is no coefficient for this regression as there is no relation between seat heating and pricing.













