---
title: "Directed Acyclic Graphs"
author: "Shashidhar Cheeti"
---

# Assignment

```{r}
# Load necessary Libraries
library(tidyverse)
library(dagitty)
library(ggdag)
library(ggrepel)
```

1. DAG for Parking Spots
```{r}
Parking_Spots <- dagify(
  Y ~ X,
  X ~ Z,
  Y ~ Z,
  coords = list(x = c(Y = 3, Z = 2, X = 1),
                y = c(Y = 0, Z = 1, X = 0)),
  labels = c("X" = "ParkingSpots",
             "Y" = "Sales",
             "Z" = "Location")
)

ggdag(Parking_Spots, text = TRUE) +
  geom_dag_point(color = "blue") +
  geom_dag_text(color = "white") +
  geom_dag_edges(edge_color = "black") +
  geom_dag_label_repel(aes(label = label))
```

2. Regression
```{r}
# Load the file
customer_sat <- readRDS("Causal_Data_Science_Data/customer_sat.rds")
# Create a Data Frame
df=data.frame(customer_sat)
```

2.1 Regress satisfaction on follow_ups 
```{r}
#lm_2_1 is the regresssion of satisfaction on follow_ups
lm_2_1 <- lm(satisfaction ~ follow_ups , data = df)
summary(lm_2_1)
```

2.2 Regress satisfaction on follow_ups and account for subscription
```{r}
#lm_2_2 is the regresssion of satisfaction on follow_ups and account for subscription
lm_2_2 <- lm(satisfaction ~ follow_ups + subscription , data = df)
summary(lm_2_2)
```

3. Comparing the coefficients: 

In the first regression with satisfaction on follow_ups are negatively correlated as increase in satisfaction with the product and service will decrease the follow_up calls to the clients.

In the second regression with satisfaction on follow_ups and account for subscription is highly correlated premium subscription levels than elite subscription levels.

4. Plot the data
```{r}
# Not conditioning on subscription
subscription_not_cond <- ggplot(df, aes(x = satisfaction, y = follow_ups)) +
  geom_point(alpha = .8) +
  stat_smooth(method = "lm", se = F)

# Conditioning on subscription 
subscription_cond <- ggplot(df, aes(x = satisfaction, y = follow_ups, color = subscription)) +
  geom_point(alpha = .8) +
  stat_smooth(method = "lm", se = F) +
  theme(legend.position = "right")

# Plot both plots
subscription_not_cond
subscription_cond
```









