---
title: "Instrumental Variables"
author: "Shashidhar Cheeti"
number-sections: false
---

# Assignment

```{r}
# Load necessary Libraries
library(tidyverse)
library(dplyr)
library(ggdag)
library(dagitty)
library(ggrepel)
```

```{r}
# Load the file
rand_enc <- readRDS("Causal_Data_Science_Data/rand_enc.rds")
# Create a Data Frame
df=data.frame(rand_enc)
head(df)
```

1. Plot DAG
```{r}
App_usuage <- dagify(
  Y ~ D,
  D ~ Z,
  coords = list(x = c(D = 0.5, Y = 2, Z = -1),
                y = c(D = 0, Y = 0, Z = 0)),
  labels = c("D" = "used_ftr",
             "Y" = "timeSpent",
             "Z" = "rand_enc")
)

ggdag(App_usuage, text = TRUE) +
  geom_dag_point(color = "blue") +
  geom_dag_text(color = "white") +
  geom_dag_edges(edge_color = "black") +
  geom_dag_label_repel(aes(label = label))
```
From my understanding of these relationships from DAG, time spent would be the outcome which depends on the used new feature (used_ftr) would be the treatment variable and randomized encouragement trial (rand_enc) would be instrumental variable.

2. Compute the naive, biased estimate.
```{r}
model_biased <- lm(time_spent ~ used_ftr, data = df)
summary(model_biased)
```

```{r}
model_naive <- lm(rand_enc ~ used_ftr, data = df)
summary(model_naive)
```

3.
```{r}
cor(df$rand_enc, df$used_ftr)
```
The positive correlation indicates that users who received the encouragement were more likely to use the new feature.

4. Compute the IV estimate using 2SLS and compare it to the naive estimate
```{r}
library(estimatr)
model_iv <- iv_robust(time_spent ~ used_ftr | rand_enc, data = df)
summary(model_iv)
```

On Computing the IV estimate using 2SLS and comparing it to the naive estimate, the naive estimate for used_ftr (0.207943) seems to be biased downward.





